Binning Strategies and Related Loss for Binned Scatterplots of Large Data

### 2016-12-04 AuthorResponseToReviewers.Rmd

- The main result from the paper is to provide simple adjustment recommendations for binning specification for reducing loss in binned scatterplots. To emphasize these recommendations, the baseball plot example in Section 5.3 has been reworked to highlight the take-home message. To your other point, we agree that future work to quantify the implicit loss of information (e.g. the imprecise ability to map continuously shaded tiles to a frequency legend) in reading binned scatterplots is needed; however, the current work strives to quantify explicit loss of information when the perception tasks are more simple (e.g. mapping distinguishably-discrete shaded tiles to an interval on the frequency legend).

### Responses to Editors Comments/Questions
*Editor's Comments to Author:*

*Associate Editor - Comments to the Author:*
*The paper in its current form does not provide a sufficiently thorough coverage of either review material or novel material to warrant publication.  However, the reviewers have some useful suggestions for ways in which a different paper (or two) could possibly be produced by expanding on different parts of this submission.*

- We hope that the revisions explanding review material and clarification of our contributions to the topic will meet the standards of your publication. An R-package with binning, loss and plotting fuctions is available through an author's Github repository; however linking directly would not allow for blinded review. As such the functions used are provided in a supplementary R file. Additionally, a zipped folder containing an Rproj file for launching the Rpackage locally can be made available if desired. If there are any additional comments, concerns or questions, our team is happy to address them.

### 2016-12-04 versionForJCGS/PaperJCGS.Rnw
Cleaning up and putting header in R scripts to be submitted to JCGS

# random bin centers
set.seed(14)
rxcent <- RandRectBin1d(x, -10, 10)
rycent <- RandRectBin1d(y, -10, 10)
# point 1 and 11 are special 
linecolor <- rep("blue", 12)
linecolor[c(1,11)] <- "red"

>>>>

# random bin centers
set.seed(14)

rxcent <- rand_rect_bin_1d(x, -10, 10, output="centers")
rycent <- rand_rect_bin_1d(y, -10, 10, output="centers")
# point 1 and 11 are special 
linecolor <- rep("blue", 12)
linecolor[c(1,11)] <- "red"
